rang: Reconstructing reproducible R computational environments with ease

### 2023-02-24 paper/paper.qmd
Switch over to quarto

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating instructions for other researchers to completely reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commericial service. The description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such.
keywords:
  - R
  - reproducibility
  - docker
date: 02 February 2023
year: 2023
bibliography: paper.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

@@

```{r, fig.cap = "The code snippet running in a R 3.5.1 container created with rang", echo = FALSE}
knitr::include_graphics("quanteda_rstudio.png", dpi = 300)
```

>>>>

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating instructions for other researchers to completely reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commericial service. The description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such.
keywords:
  - R
  - reproducibility
  - docker
year: 2023
bibliography: paper.bib
format:
  pdf: default
  arxiv-pdf:
    keep-tex: true    
---

@@

```{r}
#| fig.cap: The code snippet running in a R 3.5.1 container created with rang
#| echo: FALSE
knitr::include_graphics("quanteda_rstudio.png", dpi = 300)
```
